---
title: "R assignment week 8"
output:
  html_document:
    df_print: paged
---

Deadline for this week: 22 November 23:59. 

Before your do this assignment, please read Wickham chapter 14 (strings; online version of the book seems to have been updated to match the paper edition), complete the GitHub module "Regular expressions", and watch the instruction video for week 8 (see Canvas).

## 0) seting working directory

```{r}
setwd("~/Master/BigdataSmallData")
```


## 1) Load the tidyverse package and import the COVID-19 sample dataset
Write down your code in the grey box.

```{r, message = FALSE}
library(tidyverse)
library(stringr)
data <- read_csv("BDSD_tweets.csv")

```

## 2) Determine the length of tweets
Create a new column in your data frame called "length" that contains the number of characters (simply put) per tweet. Write down your code in the grey box.

```{r}

data <- data %>% 
  mutate(lenght = str_length(text))

```

## 3) Convert all text to lower case
When conducting text analysis, a decision that is often made is to convert all text to lowercase. Write down your code in the grey box.

```{r, include = FALSE}
# I hided the results in the markdown
str_to_lower(data$text, locale = "en")
```

## 4) Working with str_view
Explain what the purpose is of the code below.

```{r}
str_view(data$text[1], "#\\w+")

```

the code looks for a hastag in the first row of text in the dataframe.

## 5) Create a new column "hastagcount1"
Let's say we are interested in the use of hashtags by the accounts in our dataset. Create a new column "hastagcount1" that indicates whether each tweet contains a hashtag or not. Use the text column as input. Write down your code in the grey box.

```{r}

data <- data %>% 
  mutate(hastagcount1 = ifelse(str_detect(text, "#\\w+"), "1 or more", "0"))

```

## 6) Create a new column "hastagcount2"
Now also create a new column "hastagcount2" that indicates the number of hashtags used per tweet. Use the text column as input. Write down your code in the grey box.

```{r}

data <- data %>% 
  mutate(hastagcount2 = (str_count(text, "#\\w+")))

```

## 7) Matching terms
Let's say we are also interested in how often people mention "social distancing", the word traveling/travelling (taking into account British-English vs. American-English spelling), and words that start with vaccin (e.g., vaccin, vaccination). Create three new columns (i.e., "socialdis", "travel", "vaccine") that indicate how often per tweet these terms are mentioned. Use the text column as input. Write down your code in the grey box.

```{r}

data <- data %>%
  mutate(socialdis = (str_count(text, "social distancing"))) 

data <- data %>%
  mutate(travel = (str_count(text, "travel+ing")))

data <- data %>%
  mutate(vaccine = str_count(text, "vaccin.*"))  

```

## 8) Create new column "hashtagtext"
Even though the colomn already exists in the dataset, for the sake of learning new R skills, create a new column "hashtagtext" that includes all hashtags per tweet, if applicable. Use the text column as input.  Write down your code in the grey box.

```{r}

data <- data %>% 
  mutate(hashtagtext = str_extract_all(text, "#\\w+"))

```
Couldn't figure out how to go from a matrix to a tibble when simplify = T. 


## 9) Remove all @otheruser from strings
Create a new column "text2" that contains the original tweets with mentions to other twitter users (e.g, @donaldtrump, @joebiden) removed. Write down your code in the grey box.

```{r}
data <- data %>% 
  mutate(text2 = str_remove_all(text, "@\\w+"))

```

## 10) Remove all hyperlinks
Create a new column "text3" that contains the content of text2 but with all urls/hyperlinks removed. Write down your code in the grey box.

```{r}
data <- data %>% 
  mutate(text3 = gsub('http\\S+\\s*', "", text))


# alternative "http.* *"

```

```{r}
#head(data$text3, n = 50)
```


## 11) Now, knit your document. 
Submit your html file on Canvas.