---
title: "R assignment week 2"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

## 0) Setting work Directory
```{r}
setwd("~/Master/BigdataSmallData")
```

## 1) Install the tidyverse package
You will need the tidyverse package for this first assignment. Show me you know how to do this in the grey box below.  

```{r, message = FALSE}
# as tidyverse was already install on my computer I tried to find a solution 
# as it would stop running the code for the rest of the file
# code retrived from : https://stackoverflow.com/questions/4090169/elegant-way-to-check-for-missing-packages-and-install-them
# " require() basically means “try to load the package using library() and return a logical value indicating the success or failure”"
if (!require("tidyverse")) install.packages('tidyverse')
```

## 2a) Load the tidyverse package
Next, you will need to load the package in order to be able to use its functions. Show me you know how to do this in the grey box below.

```{r}
library(tidyverse)
```

## 2b) Suppress messages from being included in your Notebook
It can be quite ugly to have package loading messages in your Notebook, especially if you need to load many packages. Go to the Cheatsheet R Markdown (see course manual) and find out which option you have to add to {r} to not have those messages displayed. Copy paste the code you used for 2a of this assignment below and add this option.

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
```

## 3) Import the sample dataset
Download "BDSD_tweets.csv" from Canvas and import it into R Studio. Write down this code in the grey box.

```{r}
data <- read_csv("BDSD_tweets.csv")

```

## 4a) Determine data types
Columns are stored in R as specific data types (e.g., numeric, character, factor, etc.). Determine the "class" of the columns: (1) retweet_id, (2) text, (3) user_friends_count. Write down your code in the grey box.

```{r}
library(dplyr)
data1 <- select(data, reweet_id, text, user_friends_count)
sapply(data1, class)
```

## 4b) Explain what these data types mean

a numeric data are made of number (int or dbl(double or real nbr)) and characters are made of vector with character or strings. 


## 4c) Which "class" would make more sense for "text", and why?
I think char makes more sens as it contains text/ made out of strings.



## 5) Remove all empty colums
To clean up the data, we first would like to remove all empty columns because we will not be using them anyway. You will have to do two things: (1) determine which columns are empty and (2) write code to filter them out of the dataset. Write down your code in the grey box.

```{r}
# which columns are empty
# tried with is.na(data) --> it scanns the entire dataset and tell T or F.
is_empty <- sapply(data, function(x) all(is.na(x) | x == " "))
is_empty

# printing names of columns with value TRUE, hence empty
name_empty <- subset(is_empty, is_empty == TRUE)
name_empty


#user_time_zone is empty

# removing user_time_zone
data3 <- select(data, -user_time_zone)
# checking if the columns has been deleted
# data3_var <- sapply(data3, names)
# data3_var

```




## 6) Select only tweets that were retweeted
Let's say we are only interested in tweets that have been retweeted. Select those tweets. You may want to print the column names of the dataset first in order to determine the corresponding variable name. Write down your code in the grey box.

```{r}
retweeted <- filter(data, retweet_count > 0 | retweet_count != NA)
#checking if it worked
#retweeted

```


## 7) Create a new variable "ffratio"
We would also like to know the friend/follower ratio of each user, where friend stands for the number of accounts that the user is following and follower stands for the number of followers the user has. Create this variable. Write down your code in the grey box.

```{r}
data <- mutate(data, ffratio = user_friends_count/user_followers_count)
# note to myself if I use = then the name of my col is juste ffratio
# if i use <- the name of my col is ffratio = user_friendetc
# delete the variable ffratio <- user_friends_count/user_followers_count
# select(data, - `ffratio <- user_friends_count/user_followers_count`)
```

## 8) Create a new variable "popular"
When looking at the dataset, one thing that you may notice is that the users have very different follower counts. Create a new column “popular” that distinguishes popular users (more than 1000 followers; assign the value 1 to these accounts) from less popular users (assign the value 0 to these users). Write down your code in the grey box.

```{r}
data <- mutate(data, popular = ifelse(user_followers_count > 10000, 1, 0))

```



## 9) Now, knit your document. 
Upload your html file on Canvas.
