---
title: "extracting tweets"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

Following Peter's instruction to retrieve tweets from tweets ID for final 
project on #BlackLivesMater


#### 0) setting working directory 

```{r}
setwd("~/Master/BigdataSmallData/final")
```


```{r, message = FALSE}
library(tidyverse)
```


reading csv of blm corpus
```{r, message = FALSE}
#importing the data
blm_corpus <- read_csv("blm_corpus.csv.gz") %>% 
  #turning message_id into char in order to prevent scientific notation
  mutate(message_id = as.character(message_id))

```

#### Exploring the dataset
```{r}
blm_corpus
```

#### Counting the number of tweet that only have #balcklivesmatter --> 35'664'304 tweets

```{r}
nbr_blm <- blm_corpus %>% 
  subset(blacklivesmatter == 1) %>%
  subset(alllivesmatter == 0) %>% 
  subset(bluelivesmatter == 0) %>% 
  nrow()


```

```{r}
nbr_blm
```

Counting the number of tweets that have #Blacklivesmatter to make sure the results are coherent
```{r}
nbr_blm_2 <- blm_corpus %>% 
  subset(blacklivesmatter == 1)

nbr_blm_2
```


#### filtering only BLM and keeping only the message ID

```{r}
blm <- blm_corpus %>% 
  filter(blacklivesmatter == 1, alllivesmatter == 0, bluelivesmatter == 0) %>% 
  select(1)

blm
```

#### selecing randomly 200'000 tweet id with set.seed() that enable replication

```{r}
# making sure the selection can be replicated use set.seed
set.seed(1)

selection <- blm %>% 
  sample_n(400000)

selection

```


#### creating the file that contains the tweet id we want to extract with the API

puting id back to numeric because hydrator does not allow ""
```{r}
#deactivation scientific notation in R
options(scipen = 999)

#transforming message_id back to numeric
selection <- selection %>% 
  mutate(message_id = as.numeric(message_id))
```

creating the file for hydrator
```{r}

write.table(selection, col.names=FALSE, row.names = FALSE, "tweetids_2.txt")

```



