---
title: "R assignment week 7"
output:
  html_document:
    df_print: paged
---

Deadline for this week: 22 November 23:59. 

Before your do this assignment, please complete the GitHub module "Basic Statistics" and take a look at the PsychTeachR website for any further instruction you may need.

## 0) seting working directory

```{r}
setwd("~/Master/BigdataSmallData")
```


## 1) Load the tidyverse package and import the COVID-19 sample dataset
Write down your code in the grey box.

```{r, message = FALSE}
library(tidyverse)
data <- read_csv("BDSD_tweets.csv")
Sys.setlocale("LC_TIME", "C")
```

## 2) Recreate three earlier steps
1) From week 2, create the popular column
2) From week 5, extract the dates from the created_at column
3) From week 6, create the favoritecate column
Make sure these three columns are created in the existing dataset. Write down your code in the grey box.

```{r}
# creating the popular variable
data <- mutate(data, popular = ifelse(user_followers_count > 1000, 1, 0))

# extracting the date
data$created_at = as.character(data$created_at)
data$date <- as.Date(data$created_at, format = "%a %b %d %H:%M:%S %z %Y")

# creating the favoritecate column
data <- data %>% 
  mutate(favoritecat = case_when(
    favorite_count < 1 ~ "0",
    favorite_count >= 1 & favorite_count < 100 ~ "1-100",
    favorite_count >= 100 ~ "100 or more"
  ))



```

## 3) Compute correlations
Compute the correlations between these four variables: user_favourites_count, user_followers_count, user_friends_count, and user_listed_count. Do not forget to install and/or load any necessary packages first, if applicable of course. Write down your code in the grey box.


```{r}
# correlation
# cor() is included in R
var <- data %>% 
  select(user_favourites_count,user_followers_count,user_friends_count,user_listed_count)

mat_cor <- cor(var, method = "pearson")
mat_cor

```

```{r}
# another way 
# install.packages("corrr")
library("corrr")

mat_cor_2 <- data %>% 
  select(user_favourites_count,user_followers_count,user_friends_count,user_listed_count) %>%
  correlate()

mat_cor_2
```


## 4) Conduct an independent t-test
Conduct an independent t-test with popular being the independent variable ( = predictor) and favorite_count being the dependent variable ( = outcome). Do not forget to install and/or load any necessary packages first, if applicable of course. Write down your code in the grey box.

```{r}
# formula notation (dependent ~ independent)

t_test <- t.test(data$favorite_count ~ data$popular)
t_test


```

## 5) Conduct an ANOVA
Conduct an ANOVA with favoritecat being the independent variable ( = predictor) and retweet_count being the dependent variable ( = outcome). Do not forget to install and/or load any necessary packages first, if applicable of course. Write down your code in the grey box.

```{r}

library(stats)

anova <- aov(retweet_count ~ favoritecat, data = data)

summary(anova)


```

## 6) Conduct a linear regression analysis
Conduct an ANOVA with favorite_count and dates being the independent variables ( = predictors) and retweet_count being the dependent variable ( = outcome). Do not forget to install and/or load any necessary packages first, if applicable of course. Write down your code in the grey box.

```{r}

anova_2 <- aov(retweet_count ~ favorite_count + date, data = data)

summary(anova_2)

```

## 7) Now, knit your document. 
Submit your html file on Canvas.