---
title: "R assignment week 9"
output:
  html_document:
    df_print: paged
---

Deadline for this week: 6 December 23:59. 

Before your do this assignment, please complete the GitHub module "Topic Modeling" (see Canvas).

## 0) Setting working directory

```{r}
setwd("~/Master/BigdataSmallData")
```


## 1) Load the tidyverse, quanteda AND topicmodels packages and import the COVID-19 sample dataset
Write down your code in the grey box.

```{r, message = FALSE}

library(tidyverse)
library(quanteda)
library(topicmodels)

data <- read_csv("BDSD_tweets.csv")

```

## 2) Create a dtm and clean it up
Create a document-term matrix. Convert the text to lowercase and use stemming. Also remove stopwords and punctuation. Next, remove hashtags (e.g., #coronavirus), hyperlinks, references to other users (e.g., @otheruser), single characters (= one-character words or individual symbols) from the document-term matrix. Write down your code in the grey box.

```{r}

# 1st step: creating a text corpus 

twt_corpus <- data %>% 
  corpus(text_field = "text")


# 2nd step: creating the document-term matrix 
# removing stopwords, punctuation and converting to lowercase + stemming

dtm <- dfm(twt_corpus, tolower=T, remove = stopwords('en'), stem = T, remove_punct=T)

# removing #, hyperlinks, @, one-character words --> not sure about this part ??
dtm <- dtm %>% 
  dfm_select(min_nchar = 2) %>% 
  dfm_remove(c("#*", "@*", 'http\\S+\\s*'))


```


## 3) Run LDA
Identify 10 topics by means of the LDA function from the topicmodels package. Use alpha = 0.1 as a control parameter. For now, you do not need to know why this specific alpha level is chosen. Be aware, however, that when you change the number of topics and control parameters you will get different results. Write down your code in the grey box.

```{r}

dtm <- convert(dtm, to = "topicmodels") 

set.seed(1)

tp = LDA(dtm, method = "Gibbs", k = 10,  control = list(alpha = 0.1))

tp

```

## 4) Function set.seed necessary?
Why do you think the GitHub module recommends to run set.seed(1) before you use the LDA function?

to make sure this analysis can be reproduce exactly in the same way.

## 5a) Inspect topics
Use the terms function from the topicmodels package to print the top 10 words of all 10 topics. Write down your code in the grey box.

```{r}
terms(tp, 10)

```

## 5b) Meaning of strange characters
At least one topic contains strange characters such as ðÿ and ðÿž. What do they refer to?

I think it's the Emoji, I did not get any tho, probably did something wrong then?

## 6) Run the topics function
Use the topics function from the topicmodels package to see which topics belong to the first ten tweets. Write down your code in the grey box.

```{r}

topics <- topics(tp)
head(topics, 10)

```

## 7) Print the topic frequencies
Determine how many tweets are characterized by each topic. Write down your code in the grey box.

```{r}

# soooooo frustrating I searched such a long time for this tiny line of code hahahaha
# I think I'll always remember it :P

table(topics)


```

## 8) Add topics column to dataset
Now add a column that indicates which topic characterizes each tweet to the dataset. Because of how the dtm is filtered (e.g., single-character words have been removed), some tweets have not received a topic classification. Write down your code in the grey box.

```{r}

# how can you know which tweets then remained ? and how can we know to which tweet id it belong ? 


datamatched = docvars(dtm)[match(rownames(dtm2), docnames(dtm)),]
data2 = cbind(datamatched, tweettopics = topics(model))


```

## 9) Summarize favorite_count and retweet_count per topic
Print the means and standard errors of the favorite counts and retweet_counts per topic. Write down your code in the grey box.

```{r}

```

## 10) Conduct an ANOVA
Conduct an ANOVA to determine whether there are differences in favorite counts between the topics. COnduct post-hoc contrasts when this is the case. Write down your code in the grey box.

```{r}

```

## 11) Plot 
Plot the mean frequency counts per topic. Choose any appropriate geom. Make sure the plot is informative and looks attractive. Write down your code in the grey box.

```{r}

```

## 12) Now, knit your document. 
Submit your html file on Canvas.
